Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-02 PAPER.tex
Some changes, not all.

One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
$P_{\rm out,\alpha} = \textbf{M}_{ee}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
estimate, decreasing the value of $P_{\rm out}$. Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:

@@

We see that $P_{\rm out}$ is comprised of multiple terms. Taking the case of very large $\textbf{e}$ so that any terms involving only 
$\textbf{x}$ are small, yields:

@@

We see that our naive expression for $P_{\rm out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two 
additional terms. An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be 
zero, since foregrounds and the cosmological signal are statistically unrelated. In P64, this assumption is used, and the first 
term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.

However, deeper investigations of these terms reveal that they contain non-negligible power. In fact, foreground modes and 
signal modes are anti-correlated on average, and this negative cross-term power arises from inverting the covariance matrix $
\textbf{C}_{r}$. Mathematically, the covariance of the data plus EoR is:

@@

\noindent where the data-only term (first term) and EoR-only term (last term) are approximately diagonal matrices. The middle 
two terms, however, have a larger amount of power in their off-diagonal terms relative to their diagonal elements, since $
\textbf{e}$ and $\textbf{x}$ are statistically unrelated. Upon inversion, these off-diagonal terms become negative, driving the 
cross-terms in Equation \ref{eq:pout_expand} to have negative power. \cc{someone help me write this more elegantly...}This 
effect is explained in more depth in \citet{switzer_et_al2015}.

>>>>

One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
$P_{\rm out,\alpha} = \textbf{M}_{ee}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, the reason is because this 
expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
estimate, decreasing the value of $P_{\rm out}$. Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:

@@

We see that $P_{\rm out}$ is comprised of multiple terms. To explore cases where signal loss is strongest, we will take the case where
$\textbf{e}$ dominates, so that any terms involving only 
$\textbf{x}$ are small, yielding:

@@

We see that our naive expression for $P_{\rm out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two 
additional terms. An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be 
zero, since foregrounds and the cosmological signal are statistically uncorrelated. In P64, this assumption is used, and the first 
term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.

However, a deeper investigation of these cross-terms reveals that they can contain non-negligible power when $\textbf{R}_{r}$
is taken to be $\textbf{C}_{r}^{-1}$ and
$\textbf{C}_{r}$ is estimated from the data itself.  As shown in \citet{switzer_et_al2015}, 
$\textbf{C}_{r}^{-1}\textbf{x}$ and
$\textbf{C}_{r}^{-1}\textbf{e}$
become anti-correlated on average. This negative cross-term power arises from inverting the covariance matrix
$\textbf{C}_{r}$. Mathematically, the covariance of the data plus EoR is:

@@

\noindent and we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
an eigenbasis of $\textbf{e}$, so that $\textbf{ee}^{\dagger}$ is diagonal.
The middle 
two terms, however, can have power in their off-diagonal terms.  As shown in Appendix C of \citet{parsons_et_al2014}, the
inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\textbf{ee}^{\dagger}$) with smaller
off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms.
\cc{someone help me write this more elegantly... (not done yet)}
